### 2022-09-26 Thesis/text/methoden.tex
update to last chapter

\begin{figure}[ht]
	\includegraphics[width=1.0\textwidth]{images/nav_bt-modified.png}
	\caption{Navigation2 Behavior Tree}
	\label{fig:bt_nav}
\end{figure}
\subparagraph*{}
The behavior tree depicted in figure \ref{fig:bt_nav} is the one that is the default Nav2 behavior and has a set of recovery behaviors already implemented (spin, wait, back up, clear map). These behaviors are executed if the robot can not make progress towards the set goal. 
Nav2 uses a node lifecycle management system to start, activate, deactivate, and shut down nodes in a controlled way. The lifecycle approach allows the system degree to monitor the system node's startups, executions, and failures. 
\subparagraph*{}
With this quantity of functions and hierarchical architecture, the ROS Navigation2 stack is an excellent basis for achieving high levels of robot autonomy. The software can be modified and expanded with plugins to fit the users' needs. 
When comparing the functionalities of the software stack to the proposed autonomous system architecture in figure \ref{fig:autonomous_driving_architectures}, the things that Nav2 is missing are a system-wide supervision layer and a more deliberative approach to behavior planning, as mentioned in chapter 2.3.
\subparagraph*{}
The absence of these components leads to a limited set of circumstances in which the robot can perform navigation reliably. One of the core problems behavior-based robots face is generating a dependable environment representation. An accurate representation is the basis for the last steps in the planning part of the "Sense - Think - Act" cycle. Unforeseen events can severely limit the reliability of the environment representation without the robot being aware of it. Examples of such events currently not handled appropriately are slipping wheels, orientation changes by external influences, or undetected, more specifically, undetectable obstacles. 
%\textit{Add statistics about random sensor failures every ~10000h} 
This can lead to erratic movement of the robot, as reactive behaviors and more deliberative behaviors compete for authority over the robot's movement. By design, to allow more intelligent robot behaviors, the deliberative behavior can override commands from reactive behaviors. However, the deliberative behavior's planning is based upon a false representation of reality, leading to unsafe commands. The unsafe planning triggers reactive-type behaviors again to counteract the commands from the deliberative behavior. Even worse would be that the reactive behaviors may not get activated, and the robot continues to drive despite being unaware of the surroundings. The unsafe behavior requires a human operator would need to step in and restore the robot to full functionality by hand.

@@

\subsection{Turtlebot3}
The Turtlebot3 is a standard mobile research platform with an available ROS interface to control the robot. The robot is well integrated into the ROS ecosystem and is established in the literature as a system to develop and integrate new methods. 
The robot has two motors with attached wheel encoders to drive and steer, classifying it as a differential drive robot. A third omnidirectional wheel stabilizes the robot. 
\subparagraph*{}
The manufacturer provides an open-source model for simulating the robot in physics-based simulators like Gazebo, as depicted in figure \ref{fig:turtlebot}, which enables faster development and testing for the robot. 
\begin{center}
\begin{figure}[ht]   
	\includegraphics[width=0.7\textwidth]{images/turtlebot_sim.png}
	\caption{Turtlebot3 model in Gazebo simulator}
	\label{fig:turtlebot}
\end{figure}
\end{center}
The equipped sensors and easy simulation capabilities make the robot well suited for using the Nav2 stack and further development for behavior planning.

@@

\section{Software and Simulation}
A comparison and assessment of the behavior planning approach were made in chapter 2.4. The decision on which approach to take fell on the behavior tree method. The reason for this is mainly the increased flexibility when creating and expanding the behavior planning compared to FSMs. Also, behavior trees allow complete determinism and introspection.
%which is why POMPDs are not suitable as the behavior planning approach for the specified requirements.

@@

Groot is a software to create, edit, monitor, and debug behavior trees with a graphical user interface. The software allows the creation of behavior trees in XML files which can be directly loaded into and used by the BT.CPP library. Groot can monitor the live execution of behavior trees and allows the introspection of how the tree reacts to different scenarios.

@@

\begin{center}
\begin{table}[ht]
	\caption{Decorator Nodes in BT.CPP}
	\label{tab:versions}
	\begin{tabular}{ | m{0.2\textwidth} | m{0.25\textwidth}| m{0.25\textwidth} | m{0.2\textwidth} |} 
  	\hline
  	\textbf{Name} & \textbf{Version / Release} & \textbf{Comments} \\ 
  	\hline
  	Operating System & Ubuntu 20.04 LTS &  \\ 
  	\hline
  	ROS & ROS2 Foxy & Long-Term-Supported Distribution \\ 
  	\hline
  	Navigation2 & Foxy-devel & Newest Release for ROS2 Foxy\\
  	\hline
  	Simulation & Gazebo 11 & Determined by choice of ROS Distro \\
  	\hline  	
  	Robot & Turtlebot3 &  \\
  	\hline
  	Behavior Tree & BT.CPP 3.7 & \\
  	\hline
  	Programming Language & C++ 14 & Determined by choice of ROS Distro \\
  	\hline
  	Build System & CMake and Colcon & Determined by choice of ROS Distro \\
  	\hline
  	Development Environment & Visual Studio Code & Offers IDE debugging options for ROS \\
  	\hline
	\end{tabular}
\end{table}
\end{center}

>>>>

\begin{figure}[ht]
	\includegraphics[width=1.0\textwidth]{images/nav_bt-modified.png}
	\caption{Navigation2 Behavior Tree}
	\label{fig:bt_nav}
\end{figure}
\subparagraph*{}
The behavior tree depicted in figure \ref{fig:bt_nav} is the one that is the default Nav2 behavior and has a set of recovery behaviors already implemented (spin, wait, back up, clear map). These behaviors are executed if the robot can not make progress towards the set goal. 
Nav2 uses a node lifecycle management system to start, activate, deactivate, and shut down nodes in a controlled way. The lifecycle approach allows the system degree to monitor the system node's startups, executions, and failures. 
\subparagraph*{}
With this quantity of functions and hierarchical architecture, the ROS Navigation2 stack is an excellent basis for achieving high levels of robot autonomy. The software can be modified and expanded with plugins to fit the users' needs. 
When comparing the functionalities of the software stack to the proposed autonomous system architecture in figure 2.2, the things that Navigation2 is missing are a system-wide supervision layer and a more deliberative approach to behavior planning, as mentioned in chapter 2.3.
\subparagraph*{}
The absence of these components leads to a limited set of circumstances in which the robot can perform navigation reliably. One of the core problems behavior-based robots face is generating a dependable environment representation. An accurate representation is the basis for the last steps in the planning part of the "Sense - Think - Act" cycle. Unforeseen events can severely limit the reliability of the environment representation without the robot being aware of it. Examples of such events currently not handled appropriately are slipping wheels, orientation changes by external influences, or undetected, more specifically, undetectable obstacles. 
%\textit{Add statistics about random sensor failures every ~10000h} 
This can lead to erratic movement of the robot, as reactive behaviors and more deliberative behaviors compete for authority over the robot's movement. By design, to allow more intelligent robot behaviors, the deliberative behavior can override commands from reactive behaviors. However, the deliberative behavior's planning is based upon a false representation of reality, leading to unsafe commands. The unsafe planning triggers reactive-type behaviors again to counteract the commands from the deliberative behavior. Even worse would be that the reactive behaviors may not get activated, and the robot continues to drive despite being unaware of the surroundings. The unsafe behavior requires a human operator would need to step in and restore the robot to full functionality by hand.

@@

\subsection{Turtlebot3}
The Turtlebot3 is a standard mobile research platform with an available ROS interface to control the robot. The robot is well integrated into the ROS ecosystem and is established in the literature as a system to develop and integrate new methods. 
The robot has two motors with attached wheel encoders to drive and steer, classifying it as a differential drive robot. A third omnidirectional wheel stabilizes the robot. 
\subparagraph*{}
The manufacturer provides an open-source model for simulating the robot in physics-based simulators like Gazebo, as depicted in figure \ref{fig:turtlebot}, which enables faster development and testing for the robot. 
\begin{center}
\begin{figure}[ht]   
	\includegraphics[width=0.5\textwidth]{images/turtlebot_sim.png}
	\caption{Turtlebot3 model in Gazebo simulator}
	\label{fig:turtlebot}
\end{figure}
\end{center}
The equipped sensors and easy simulation capabilities make the robot well suited for using the Nav2 stack and further development for behavior planning.

@@

\section{Software and Simulation}
A comparison and assessment of the behavior planning approach were made in chapter 2.4. The decision on which approach to take fell on the behavior tree method. The reason for this is mainly the increased flexibility when creating and expanding the behavior planning compared to FSMs. Also, behavior trees allow complete determinism and introspection which is why POMPDs are not suitable as the behavior planning approach for the specified requirements.

@@

Groot is a software to create, edit, monitor, and debug behavior trees with a graphical user interface. The software allows the creation of behavior trees in XML files which can be directly loaded into and used by the BT.CPP library. Groot can monitor the live execution of behavior trees and allows the introspection of how the tree reacts to different scenarios (compare fig. \ref{fig:groot}).

\begin{center}
	\begin{figure}[ht]   
		\includegraphics[width=0.7\textwidth]{images/groot.png}
		\caption{Live monitoring of behavior trees with Groot}
		\label{fig:groot}
	\end{figure}
\end{center}

@@

\begin{center}
\begin{table}[ht]
	\caption{Used Software Versions}
	\label{tab:versions}
	\begin{tabular}{ | m{0.2\textwidth} | m{0.25\textwidth}| m{0.25\textwidth} | m{0.2\textwidth} |} 
  	\hline
  	\textbf{Name} & \textbf{Version / Release} & \textbf{Comments} \\ 
  	\hline
  	Operating System & Ubuntu 20.04 LTS &  \\ 
  	\hline
  	ROS & ROS2 Foxy & Long-Term-Supported Distribution \\ 
  	\hline
  	Navigation2 & Foxy-devel & Newest Release for ROS2 Foxy\\
  	\hline
  	Simulation & Gazebo 11 & Determined by choice of ROS Distro \\
  	\hline  	
  	Robot & Turtlebot3 &  \\
  	\hline
  	Behavior Tree & BT.CPP 3.7 & \\
  	\hline
  	Programming Language & C++ 14 & Determined by choice of ROS Distro \\
  	\hline
  	Build System & CMake and Colcon & Determined by choice of ROS Distro \\
  	\hline
  	Development Environment & Visual Studio Code & Offers IDE debugging options for ROS \\
  	\hline
	\end{tabular}
\end{table}
\end{center}
